Convex Surrogates via Polyhedral Losses

### 2019-02-02 cvx-fin.tex
related work

Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space. (\cite{frongillo2015elicitation,  ramaswamy2016convex}) \raf{cite}
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~(\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent})\raft{cite}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.~\cite{crammer2001algorithmic}\raft{cite}
\bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}

@@

\subsection{Related works}
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.

  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}

%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.

  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.

  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works, to our knowledge, that generalizes the construction of convex surrogates beyond the binary outcome setting comes from~\cite{ramaswamy2018consistent}-- originally appearing in 2014.
  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.

  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}

  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.

>>>>

Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
A growing body of research is concerned with designing and analyzing convex surrogates for given loss functions, and more broadly, understanding when such surrogates can and cannot be found.\raf{cite}
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space.\raf{cite}
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)\raf{cite}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one \emph{embeds} a discrete loss function into a real vector space so that it can be convexified.
Special cases include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.\raf{cite}
\bo{it felt like the following results were only a warmup instead of main results. Not sure how to change this, maybe a paragraph break helps.}

@@

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \citet{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
%
%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
%  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
%
%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
%
%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
%
%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent} (originally 2014), who give an embedding of the \emph{abstain loss} into very few dimensions.
For the case of $\reals^2$, we will show that no embedding can do better.
%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
%
%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
%
  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g. $0-1$ loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method.
  However, we will mention relevant results inline.
%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.
